---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warnings = FALSE, 
  messages = FALSE, 
  prompt = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


  [![Codecov test coverage](https://codecov.io/gh/TonyLadson/Palindrome/branch/main/graph/badge.svg)](https://app.codecov.io/gh/TonyLadson/Palindrome?branch=main)
  
  
# Palindrome

This package contains a single function: Make_palindrome.  A palindrome number is the same when read forward or backward e.g. 121.  

One obscure mathematical recreation is to make non-palindrome numbers palindromic through a process of reversing and adding.

Choose a number

1. If it’s a palindrome, then stop
2. If not, reverse the number and add to the original number
3. Go to step 2.

For example: 12 + 21 = 33

Most numbers become palindromes quite quickly but some take a while, for example, the numbers 89 and 98 take 24 iterations.  No one has yet made 196 palindromic  using this procedure despite years of reversing and adding.  There are a couple of web sites that have way-more information about this than you’d probably care to know: [196 Palindrome Quest](http://jasondoucette.com/worldrecords.html#196) and [p196](http://www.p196.org/). A number that cannot be made into a palindrome by the process of reversing and adding is referred to a  [Lychrel](https://en.wikipedia.org/wiki/Lychrel_number number).

More information [here](https://tonyladson.wordpress.com/2013/03/14/palindrome-numbers/)


## First things first

`Palindrome` is a toy project and is still under development. You can install the latest version from [GitHub](https://github.com/) with:

```{r, install, results = "hide", eval = FALSE}
# install.packages("remotes")
remotes::install_github("TonyLadson/Palindrome")
```

## Take it for a spin

Try Make_palindrome(89)

```{r example}
library(Palindrome)
 
Make_palindrome(89)
```

